---
title: "Jira Trend"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
#library(stringr)
#install.packages("skimr")
library(skimr)

theme_set(theme_light())

```

This report is a delivery output of managed service. 

# JIRA Perspectives

There are 238 columns in orignal jira colums, but we only extract `Status`, `Priority`, `Assignee`, `Creator`, `Created`, `Resolved`. 
This Dataset was extracted from jira pages with query of ????
  

```{r}

all_jira <- read_csv("C:/Users/InchulJung/Downloads/JIRA (8).csv")


jira <- all_jira %>%
  janitor::clean_names() %>%
  select (status, priority, assignee, creator, created, resolved) %>%
  mutate(created = dmy_hm (created)) %>%
  filter(created > ymd("2020-06-30")) %>%
  mutate(resolved = dmy_hm (resolved),
         assignee = ifelse(is.na(assignee),"None", assignee),
         status = as.factor(status),
         priority = as.factor(priority),
         month = lubridate::month(created),
         month = as.factor(month),
         year = lubridate::year(created),
         year = as.factor(year)) %>%
  mutate (resolved = case_when(is.na(resolved) ~ lubridate::now(), 
                      TRUE ~ resolved)) 

glimpse(jira)

skim(jira)

```


Data features are like : 

```{r}

## preprcessing data - ex) imputate for NA data with today of resolved

report_year=2020
report_month = 12

jira %>%
  summary() 

```



# ACC Analysis 
```{r}
jira %>%
  group_by(year, month) %>%
  summarise(n = n())

#jira count percent per month/year
jira %>%
  count(year, month) %>%
  add_count(percent = n/sum(n)) %>%
  ggplot(aes(month, percent)) + 
  geom_col(show.legend = FALSE) +
  scale_y_continuous(labels=scales::percent_format()) +
  facet_grid(year~.) +
  labs(title= "JIRA Creating Trend per month")
  
```



## Monthly Trend of JIRA opening

```{r}
jira %>%  
  ggplot(aes(month, fill=month)) +  geom_bar(show.legend = FALSE) + 
  facet_grid(year~.) + 
  labs(title= "JIRA Creating Trend per month")
  
```
### JIRA status
```{r}

jira %>% 
  ggplot(aes(month,fill=status)) + geom_bar(position=position_dodge( preserve = c("single"))) + 
  facet_grid(year~.) +
  labs(title= "Status Trend per month")
```


```{r}
jira %>%
  ggplot(aes(month, fill=status)) + geom_bar()

jira %>% 
  ggplot(aes(status, fill=status)) + geom_bar(show.legend = FALSE) + 
  coord_flip() + 
  facet_wrap(year~month, nrow = 2, scales = "free_x") +
  labs(title= "Status Trend per month")


jira %>% 
  ggplot(aes(status, fill=status)) + 
  geom_bar(show.legend = FALSE) +
  coord_flip() +
  facet_grid(year~month, scales = "free_x") +
  labs(title= "Status Trend per month") 
  
```


## JIRA Priority
```{r}

jira %>% 
  ggplot(aes(month, fill=priority)) + geom_bar() + facet_wrap(~year, nrow=2) + labs(title= "Priority Trend per month")


```


## JIRA Creators
```{r JIRA Creators, eval=FALSE, include=FALSE}

jira %>%
  filter(year==2020, month==7) %>%
  mutate(assignee=fct_lump_n(assignee,2)) %>%
  count(year, month, assignee, sort=TRUE) 

jira %>%
  group_by (year, month) %>%
  count(assignee, sort=TRUE) %>%
  mutate(assignee=fct_lump_n(assignee,2,w=n)) %>%
  count(assignee, sort=TRUE, wt=n) %>%
  arrange(year, month)

jira %>%
  count(year, month, assignee, sort=TRUE) %>%
  mutate(assignee=fct_lump_n(assignee,2,w=n)) %>%
  count(assignee, sort=TRUE, wt=n) %>% 
  arrange(year, month)
## => after "count", it does not have "group" attrubte. 


jira %>%
  group_by (year, month) %>%
  count(assignee, sort=TRUE) %>%
  mutate(assignee=fct_lump_n(assignee,2,w=n)) %>%
  count(assignee, sort=TRUE, wt=n) %>%
  ggplot(aes(n, fct_reorder(assignee,n), fill=assignee)) + 
  geom_col(show.legend = FALSE) +
  facet_wrap(year~month, scale="free_y") +
  labs(x="", 
       y="",
       title = "The most assinged person lumped")

#final output

jira %>%
  count(year, month, assignee) %>%
  add_count(assignee, wt=n) %>%
  ggplot(aes(n, fct_reorder(assignee,nn), fill=assignee)) + 
  geom_col(show.legend = FALSE) + 
  facet_grid(year~month, scale="free") + 
  labs(x="", 
       y="",
       title = "The most assinged person per month")

```

```{r}
jira %>% 
  filter(assignee %in% c("Inchul Jung", "Don Chan", "Sushil Shirke", "Seun Kehinde", "Joe Owenson")) %>%
  count(year, month, assignee, sort=TRUE) %>%
  add_count(assignee, wt=n) %>%
  ggplot(aes(n, fct_reorder(assignee,nn), fill=assignee)) + 
  geom_col(show.legend = FALSE) + 
  facet_wrap(year~month, scale="free") + 
  labs(x="", 
       y="",
       title = "The most assinged person per month (Only Servians)")
```


## Average Resolving Time
```{r Average Resolving, echo=FALSE, message=FALSE, warning=FALSE}

jira %>% 
  filter (status == "Done") %>%
  mutate(duration = difftime(resolved, created, units = "days")) %>%
  ggplot(aes(month, duration, fill=month)) + 
  geom_boxplot(show.legend = FALSE, na.rm=TRUE, outlier.shape = NA) +
  geom_point(aes(y=duration), alpha=0.2, show.legend = FALSE) + 
  geom_jitter(show.legend = FALSE) + 
  facet_grid(year~.) +
  labs(x="", y="days", 
       title = "Resolving trend")


servians_user <- c("Inchul Jung", "Don Chan", "Sushil Shirke", "Seun Kehinde", "Joe Owenson")

jira %>% 
  filter(status == "Done") %>%
  filter(assignee %in% servians_user) %>%
  mutate(team="servians") 

team_group <- jira %>% 
  filter(status == "Done") %>%
  mutate(team=ifelse(assignee %in% servians_user, "servian", "other")) 



team_group %>% 
  filter (status == "Done") %>%
  mutate(duration = difftime(resolved, created, units = "days")) %>%
  ggplot(aes(team, duration, fill=team )) + 
  geom_boxplot(show.legend = FALSE, na.rm=TRUE) +
  facet_grid(year~month) +
  labs(x="", y="days", 
       title = "Resolving trend",
       subtitle = "only servian users")
```


```{r}

jira %>% 
  filter(status == "Done") %>%
  filter(assignee %in% c("Inchul Jung", "Don Chan", "Sushil Shirke", "Seun Kehinde", "Joe Owenson")) %>%  
  mutate(duration = difftime(resolved, created, units = "days")) %>%
  ggplot(aes(month, duration, fill=month)) + 
  geom_boxplot(show.legend = FALSE, na.rm=TRUE) +
  geom_point(aes(y=duration), alpha=0.5, show.legend = FALSE) + 
  geom_jitter(show.legend = FALSE) + 
  facet_wrap(~year) + 
  labs(x="", y="days", 
       title = "Resolving trend",
       subtitle = "Only for Servians")

```
